Report: Complex Support Vector Detector for Large MIMO System

### 2015-11-09 Report Aug 5 2015/Report Aug 2015.tex
simulation result for MMSE MMSE-OSIC MMSE-AOMIC, MMSE-OMIC, RSVD, RSVD-OMIC
Thesis Introduction

This inequalities (also called saddle point conditions) yield KKT conditions (see Theorem 6.26 \cite{scholkopf2002learning}), which are 

@@

>>>>

These inequalities (also called saddle point conditions) holds if and only if KKT conditions holds (see Theorem 6.26 \cite{scholkopf2002learning}), which are 

@@

Therefore, KKT conditions are the necessary and sufficient conditions for optimality.
